Bird beak's elaboration and exploration

### 2022-03-10 Analysis/04-Figure1.Rmd
rearranged Analysis folder

box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure1_phylo_Dplot.pdf", height = box_size*1, width = box_size*1)

@@

    ## Calculate which dimension contains the most variance
    add.dims(superorder_shapespace, name.col)
    n <- 1000
    covars_cent_tend <- lapply(sample.n(get.subsets(superorder_shapespace, subset = names(name.col))$covar, n), VCV.cent.tend, mean)
    dim_var <- apply((get.one.axis(covars_cent_tend[[1]], axis = 1, level = 0.95)), 2, dist)
    text(0,0.3, paste0(names(name.col), " (", which(dim_var == max(dim_var)), ")"), cex = 1, col = name.col)
    # text(0,0.3, paste0(names(name.col)), cex = 1.2, col = name.col)

@@

    ## Calculate which dimension contains the most variance
    add.dims(order_shapespace, name.col)
    n <- 1000
    covars_cent_tend <- lapply(sample.n(get.subsets(order_shapespace, subset = names(name.col))$covar, n), VCV.cent.tend, mean)
    dim_var <- apply((get.one.axis(covars_cent_tend[[1]], axis = 1, level = 0.95)), 2, dist)
    text(0,0.3, paste0(names(name.col), " (", which(dim_var == max(dim_var)), ")"), cex = 1, col = name.col)
    # text(0,0.3, paste0(names(name.col)), cex = 1.2, col = name.col)

>>>>

box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure1_phylo_Dplot.pdf", height = box_size*2, width = box_size*2)

@@

    ## Calculate which dimension contains the most variance
    add.dims(superorder_shapespace, name.col)
    n <- 1000
    covars_cent_tend <- lapply(sample.n(get.subsets(superorder_shapespace, subset = names(name.col))$covar, n), VCV.cent.tend, mean)
    dim_var <- apply((get.one.axis(covars_cent_tend[[1]], axis = 1, level = 0.95)), 2, dist)
    # text(0,0.3, paste0(names(name.col), " (", which(dim_var == max(dim_var)), ")"), cex = 1, col = name.col)
    text(0,0.3, paste0(names(name.col)), cex = 1.2, col = name.col)

@@

    ## Calculate which dimension contains the most variance
    add.dims(order_shapespace, name.col)
    n <- 1000
    covars_cent_tend <- lapply(sample.n(get.subsets(order_shapespace, subset = names(name.col))$covar, n), VCV.cent.tend, mean)
    dim_var <- apply((get.one.axis(covars_cent_tend[[1]], axis = 1, level = 0.95)), 2, dist)
    # text(0,0.3, paste0(names(name.col), " (", which(dim_var == max(dim_var)), ")"), cex = 1, col = name.col)
    text(0,0.3, paste0(names(name.col)), cex = 1.2, col = name.col)

### 2022-03-10 Analysis/Older_ideas/04-full_analyses_run.Rmd
rearranged Analysis folder

```{r, run param chains}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = chara_data,
                                   dimensions   = c(1:17),
                                   tree         = chara_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 5000000,
                                       thin   = 1000,
                                       burnin = 0))

>>>>

## Check the following options:

 * saving parameters
 * number of dimensions
 * numbers of iterations (especially rate)
 * check options in brms

```{r, run param chains}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = chara_data,
                                   dimensions   = c(1:17),
                                   tree         = chara_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 5000000,
                                       thin   = 5000,
                                       burnin = 0))
